Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in Bangladesh: an online survey

### 2021-10-28 code/processing_code/processingscript.Rmd
more exploratory analysis + manuscript update
.

#load needed packages. make sure they are installed.
```{r}
library(readxl) #for loading Excel files
library(dplyr) #for data processing
library(here) #to set paths
```

@@

# save data as RDS
# I suggest you save your processed and cleaned data as RDS or RDA/Rdata files. 
# This preserves coding like factors, characters, numeric, etc. 
# If you save as CSV, that information would get lost.
# See here for some suggestions on how to store your processed data:
# http://www.sthda.com/english/wiki/saving-data-into-r-data-format-rds-and-rdata

@@

>>>>

#load needed packages. make sure they are installed.
```{r}
library(readxl) #for loading Excel files
library(dplyr) #for data processing
library(here) #to set paths
library(tidyverse)
```

@@

@@

```{r}
processeddata2 <- processeddata %>%
                  mutate (infection_status_info = factor(infection_status_info)) 
```

```{r}
str(processeddata2)
```

```{r}
save_data_location <- here::here("data","processed_data","processeddata2.rds")
```

### 2021-10-28 products/manuscript/Manuscript.Rmd
.

```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable, caption = 'Age Percentage of Participants.')
```
78.9% of total participants are less than or equal  to 35 years old.

```{r summarytable2,  echo=FALSE}
resulttable=readRDS("../../results/summarytable2.rds")
knitr::kable(resulttable, caption = 'Sex Percentage of Participants.')
```

```{r summarytable3,  echo=FALSE}
resulttable=readRDS("../../results/summarytable3.rds")
knitr::kable(resulttable, caption = 'Education Background Percentage of Participants.')
```

```{r summarytable4,  echo=FALSE}
resulttable=readRDS("../../results/summarytable4.rds")
knitr::kable(resulttable, caption = 'Income Percentage of Participants.')
```

```{r summarytable5,  echo=FALSE}
resulttable=readRDS("../../results/summarytable5.rds")
knitr::kable(resulttable, caption = 'Residence Percentage of Participants.')
```

```{r summarytable6,  echo=FALSE}
resulttable=readRDS("../../results/summarytable6.rds")
knitr::kable(resulttable, caption = 'Source of information Percentage of Participants.')
```

```{r summarytable7,  echo=FALSE}
resulttable=readRDS("../../results/summarytable7.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants working from home or not.')
```

```{r summarytable8,  echo=FALSE}
resulttable=readRDS("../../results/summarytable8.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants quarantined or not at some stage.')
```

```{r summarytable9,  echo=FALSE}
resulttable=readRDS("../../results/summarytable9.rds")
knitr::kable(resulttable, caption = 'Percentage of covid test status of the participants.')
```

```{r summarytable10,  echo=FALSE}
resulttable=readRDS("../../results/summarytable10.rds")
knitr::kable(resulttable, caption = "Percentage of participants' worry level about (re)infection with COVID-19.")
```

```{r summarytable11,  echo=FALSE}
resulttable=readRDS("../../results/summarytable11.rds")
knitr::kable(resulttable, caption = "Percentage of participants' history of chronic disease")
```

_Continue by creating plots or tables of the outcome(s) of interest and the predictor/exposure/input variables you are most interested in. If your dataset is small, you can do that for all variables. Plots produced here can be scatterplots, boxplots, violinplots, etc. Tables can be simple 2x2 tables or larger ones._

>>>>

```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable, caption = 'Age Percentage of Participants.')
```
**78.9% of total participants are less than or equal  to 35 years old.**

```{r summarytable2,  echo=FALSE}
resulttable=readRDS("../../results/summarytable2.rds")
knitr::kable(resulttable, caption = 'Sex Percentage of Participants.')
```
**While 45.18% of the participants were female, 54.82% were male.**

```{r summarytable3,  echo=FALSE}
resulttable=readRDS("../../results/summarytable3.rds")
knitr::kable(resulttable, caption = 'Education Background Percentage of Participants.')
```
**78.05% of the participants had a bachelor or post-bachelor degree**
```{r summarytable4,  echo=FALSE}
resulttable=readRDS("../../results/summarytable4.rds")
knitr::kable(resulttable, caption = 'Income Percentage of Participants.')
```
**Almost 50% of the participants belongs to "upper middle income category"**
```{r summarytable5,  echo=FALSE}
resulttable=readRDS("../../results/summarytable5.rds")
knitr::kable(resulttable, caption = 'Residence Percentage of Participants.')
```
**Less than 10% of the participants live in a village/rural area**
```{r summarytable6,  echo=FALSE}
resulttable=readRDS("../../results/summarytable6.rds")
knitr::kable(resulttable, caption = 'Source of information Percentage of Participants.')
```
**Health professionals and Tv/radio seems to be the most trusted source to the participants.**
```{r summarytable7,  echo=FALSE}
resulttable=readRDS("../../results/summarytable7.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants working from home or not.')
```
**Apparently equal half of the participants worked from or not**
```{r summarytable8,  echo=FALSE}
resulttable=readRDS("../../results/summarytable8.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants quarantined or not at some stage.')
```
**Major half of the participants did quarantine at some stage during the study**
```{r summarytable9,  echo=FALSE}
resulttable=readRDS("../../results/summarytable9.rds")
knitr::kable(resulttable, caption = 'Percentage of covid test status of the participants.')
```
**63% of the participants didn't go through a COVID test**
```{r summarytable10,  echo=FALSE}
resulttable=readRDS("../../results/summarytable10.rds")
knitr::kable(resulttable, caption = "Percentage of participants' worry level about (re)infection with COVID-19.")
```
**Almost half of the participants (46%) were moderate or more worried about reinfection**
```{r summarytable11,  echo=FALSE}
resulttable=readRDS("../../results/summarytable11.rds")
knitr::kable(resulttable, caption = "Percentage of participants' history of chronic disease")
```
**Only 22% of the participants recorded to have some sort of chronic disease**
_Continue by creating plots or tables of the outcome(s) of interest and the predictor/exposure/input variables you are most interested in. If your dataset is small, you can do that for all variables. Plots produced here can be scatterplots, boxplots, violinplots, etc. Tables can be simple 2x2 tables or larger ones._
